Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with \pkg{ACSNMineR} and \pkg{RNaviCell} packages

### 2016-05-16 jss/Deveau.tex
updated publication
[skip ci]

%% for pretty printing and a nice hypersummary also set:
\author{by Paul Deveau, Emmanuel Barillot, Valentina Boeva, Andrei Zinovyev and Eric Bonnet} %% comma-separated
\title{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with ACSNMineR and RNaviCell packages} %% without formatting
%\Shorttitle{Module Enrichment and Data Visualization with ACSNMineR and RNaviCell} %% a short title (if necessary)
\maketitle
%% publication information

>>>>

%% for pretty printing and a nice hypersummary also set:
\author{by Paul Deveau, Emmanuel Barillot, Valentina Boeva, Andrei Zinovyev and Eric Bonnet} %% comma-separated
\title{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with \pkg{ACSNMineR} and \pkg{RNaviCell} packages} %% without formatting
%\Shorttitle{Module Enrichment and Data Visualization with ACSNMineR and RNaviCell} %% a short title (if necessary)
\maketitle
%% publication information
